test flashr2

### 2017-09-16 analysis/flash_beta_test.Rmd
Files commited by wflow_commit.

```{r}
library(PMA)
library(softImpute)
set.seed(999)
N = 100
P = 200
dat = sim_K(K=1,N, P, SF = 0.5, SL = 0.5, signal = 1,noise = 5)
# a = rchisq(N,3)
# b = rchisq(P,1)
# data = sim_hd(N, P, SF = 0.5, SL = 0.5, signal = 1, a ,b,mu = 0)
Y = dat$Y
```

@@

@@

>>>>

I print the obj value to check if it is increase.

```{r}
library(PMA)
library(softImpute)
set.seed(999)
N = 100
P = 200
dat = sim_K(K=1,N, P, SF = 0.5, SL = 0.5, signal = 1,noise = 5)
# a = rchisq(N,3)
# b = rchisq(P,1)
# data = sim_hd(N, P, SF = 0.5, SL = 0.5, signal = 1, a ,b,mu = 0)
Y = dat$Y
Y_miss = Y
Y_miss[1:50,1:100] = NA
Y_miss[51:100,101:200] = NA
```

@@

### for this case, when data are missing, the obj is not increase

the final result is rank zero, so I am not sure it is a problem

```{r}
data.miss = set_flash_data(Y_miss)
g1.miss = flash_r1(data.miss,verbose=TRUE)
```

@@

In this case, I have two problems:

1. The Obj function seems not increasing.

2. the RMSE seems a bit large for flashr2. I think the $\tau$ estimation is not that precise.
